### 2018-02-01 includes/stringfuzz.tex

\begin{table}[t]
    \caption{\fuzzer{} built-in (a) generators and (b) transformers.}
    \begin{subtable}{1\textwidth}
        \centering
        \caption{\generator{} built-in generators.}
        \label{tbl:generators}
        \begin{tabular}{ l l }
            \toprule
            \textbf{Name}
            & \textbf{Generates instances that have ...} \\
            \midrule
            \textit{Concats}
            & Long concats and optional random extracts. \\
            \textit{Lengths}
            & Many variables (and their concats) with length constraints. \\
            \textit{Overlaps}
            & An expression of the form A.X = X.B. \\
            \textit{Equality}
            & An equality among concats, each with variables or constants. \\
            \textit{Regex}
            & Regexes of varying complexity. \\
            \textit{Random-Text}
            & Random, likely syntactically \textit{in}valid text. \\
            \textit{Random-AST}
            & Random, but semantically \textit{valid} text. \\
            \bottomrule
        \end{tabular}
    \end{subtable}
    \begin{subtable}{1\textwidth}
        \centering
        \caption{\transformer{} built-in transformers.}
        \label{tbl:transformers}
        \begin{tabular}{l l}
            \toprule
            \textbf{Name}
            & \textbf{The transformer ...} \\
            \midrule
            \textit{Fuzz}
            & Replaces literals and operators with similar ones.\\
            \textit{Graft}
            & Randomly swaps non-leaf nodes with leaf nodes.\\
            \textit{Multiply}\footnote{Satisfiable inputs 
            will produce satisfiable outputs (see Appendix).}
            & Multiplies integers and repeats strings by N.\\
            \textit{Nop}
            & Does nothing (can translate between \smtfull{}).\\
            \textit{Reverse}\footnote{Input and output 
            instances will be equisatisfiable (see Appendix).}
            & Reverses all string literals and concat arguments.\\
            \textit{Rotate}
            & Rotates compatible nodes in syntax tree.\\
            \textit{Translate}\footnotemark[4]
            & Permutes the alphabet.\\
            \textit{Unprintable}
            & Replaces characters in literals with unprintable ones.\\
            \bottomrule
        \end{tabular}
    \end{subtable}
\end{table}

>>>>

\begin{table}[t]
    \caption{\fuzzer{} built-in (a) generators and (b) transformers.}
    \begin{subtable}{1\textwidth}
        \centering
        \caption{\generator{} built-in generators.}
        \label{tbl:generators}
        \begin{tabular}{ l l }
            \toprule
            \textbf{Name}
            & \textbf{Generates instances that have ...} \\
            \midrule
            \textit{Concats}
            & Long concats and optional random extracts. \\
            \textit{Lengths}
            & Many variables (and their concats) with length constraints. \\
            \textit{Overlaps}
            & An expression of the form A.X = X.B. \\
            \textit{Equality}
            & An equality among concats, each with variables or constants. \\
            \textit{Regex}
            & Regexes of varying complexity. \\
            \textit{Random-Text}
            & Random, likely syntactically \textit{in}valid text. \\
            \textit{Random-AST}
            & Random, but semantically \textit{valid} text. \\
            \bottomrule
        \end{tabular}
    \end{subtable}
    \begin{subtable}{1\textwidth}
        \centering
        \caption{\transformer{} built-in transformers.}
        \label{tbl:transformers}
        \begin{tabular}{l l}
            \toprule
            \textbf{Name}
            & \textbf{The transformer ...} \\
            \midrule
            \textit{Fuzz}
            & Replaces literals and operators with similar ones.\\
            \textit{Graft}
            & Randomly swaps non-leaf nodes with leaf nodes.\\
            \textit{Multiply}\footnote{Satisfiable inputs 
            will produce satisfiable outputs (see Appendix for proof).}
            & Multiplies integers and repeats strings by N.\\
            \textit{Nop}
            & Does nothing (can translate between \smtfull{}).\\
            \textit{Reverse}\footnote{Input and output 
            instances will be equisatisfiable (see Appendix for proof).}
            & Reverses all string literals and concat arguments.\\
            \textit{Rotate}
            & Rotates compatible nodes in syntax tree.\\
            \textit{Translate}\footnotemark[4]
            & Permutes the alphabet.\\
            \textit{Unprintable}
            & Replaces characters in literals with unprintable ones.\\
            \bottomrule
        \end{tabular}
    \end{subtable}
\end{table}
